# Loading the Data and Preprocessing the tables for SCM Predictors.

```{r}
# Loading the required libraries.
library(tidyverse)
library(readxl)
library(dplyr)
library(ggplot2)
library(readr)

```


# Predictor Datasets 
```{r}
sgr_cp_97_16 <- read_csv("C:\\Users\\Akash Mittal\\Documents\\GitHub\\Causal Inference\\Crime against Women\\Final Ones\\Additional DataSets\\Growth Rates 2001-2014\\State UTs wise Growth Rate - GSDP % (Constant Prices) from 1997-98 to 2015-2016.csv") # data for State UT's Growth Rate 

lr_01_15 <- read_csv("C:\\Users\\Akash Mittal\\Documents\\GitHub\\Causal Inference\\Crime against Women\\Final Ones\\Additional DataSets\\Literacy Rates\\StateUTs-wise Literacy Rates as per Census 2001 and 2011.csv") # data for Literacy Rate

pc_income <- read_excel("C:\\Users\\Akash Mittal\\Documents\\GitHub\\Causal Inference\\Crime against Women\\Final Ones\\Additional DataSets\\Per_Capita Income\\Per_Capita_Income_2004-2020.xlsx") # data for Per Capita Income

```

### Processing data for State Domenstic Growth Rates
#### Cleaning the Data

```{r}
years <- paste0(1997:2016)

# Combine with the "State" column
colnames(sgr_cp_97_16) <- c("State", years)


```

#### Converting to Long Format
```{r}

sgr_cp_long_data <- sgr_cp_97_16 %>%
  gather(key = "Year", value = "SDP_GrowthRate", -State)

sgr_cp_long_data <- sgr_cp_97_16 %>%
  mutate(Predictor = "SDP_Growth Rate") %>%
  gather(key = "Year", value = "Value", -State, - Predictor)

```

#### Unique State Names
```{r}
# Unique Names of States used for Standardization
unique(sgr_cp_long_data$State)
```

### Processing data for Literacy Rate (the rates from census were available for 2001 and 2011, for the remaining years, the rates have been estimated)
#### Cleaning the data

```{r}
View(lr_01_15)
str(lr_01_15)
```

#### converting to the Long Format

```{r}
lr_long_data <- lr_01_15 %>%
  select(-CAGR, -`Sl. No.`) %>%
  mutate(Predictor = "Literacy Growth Rate") %>%
  gather(key = "Year", value = "Value", -`India/States/UTs`, -Predictor)

colnames(lr_long_data) <- c("State", "Predictor", "Year", "Value")
```

#### Unique State Names

```{r}
unique(lr_long_data$State)
```

### Processing the data for Per-Capita Income
Note: Data is available from 2004 onwards only.

```{r}

View(pc_income)
head(pc_income)
```

#### Already in Long Format, and standardizing the Variable Names
```{r}
# Cleaning Data
pc_income <- pc_income %>%
  mutate(Year = as.numeric(sub("-.*", "", Year))) #Remove everything after -, and then converting year to numeric

# Remove rows where 'Year' is NA (these are additional comment rows in dataset.)
pc_income <- pc_income %>%
  filter(!is.na(Year))  # Keeps only rows where 'Year' is not NA

```


```{r}
head(pc_income)
```


#### Unique State Names

```{r}
unique(pc_income$State)
```
### Combining the Three data frames into one Predictor dataframe
##### But lets correct the state names in the different datasets


```{r}

# to substiture using gsub(pattern, replacement, x) (global substitution)

lr_long_data$State <- gsub("Chattisgarh", "Chhattisgarh", lr_long_data$State)
lr_long_data$State <- gsub("Jammu & Kashmir", "Jammu and Kashmir", lr_long_data$State)
lr_long_data$State <- gsub("Orissa", "Odisha", lr_long_data$State)

pc_income$State <- gsub("Uttrakhand", "Uttarakhand", pc_income$State)
unique(pc_income$State)

```

```{r}
sgr_cp_long_data$Year = as.numeric(sgr_cp_long_data$Year)
lr_long_data$Year = as.numeric(lr_long_data$Year)

```

```{r}
pc_income <- pc_income %>%
  rename(
    State = `State`,
    Year = `Year`,
    Predictor = `Price Category`,
    Value = `Price (in ₹)`
  ) %>%
  select(State, Predictor, Year, Value)  # Ensuring the columns are in the correct order

head(pc_income)
```

#### Combining all the dataframes

```{r}
predictor_df <- bind_rows(sgr_cp_long_data, lr_long_data, pc_income)

View(predictor_df)
#unique(predictor_df$Predictor)

predictor_df$Predictor <- recode(predictor_df$Predictor,
                                  "current" = "Per Capita Income_Current",
                                  "constant" = "Per Capita Income_Constant")

```


# End of Part to prepare the Dataset for Predictor Variables

# Prepare dataset for Road Accidents (as required for a falsification test)

### Loading and Processing the datasets for Accidents

```{r}

# The below datasets have many different crime data, but my focus point is to gather the data for murders

accidents_01_15 <- read_csv("C:\\Users\\Akash Mittal\\Documents\\GitHub\\Causal Inference\\Crime against Women\\Final Ones\\Additional DataSets\\Traffic Accidents\\StateUT wise total no of road accidents during 2001-2015.csv")

```


```{r}
head(accidents_01_15)
```

#### Converting to Long Format
```{r}

accidents_long <- accidents_01_15 %>%
  mutate(Crime_Head = "Total Accidents") %>%
  gather(key="Year", value="Value", -`States/UTs`, -Crime_Head)
  

str(accidents_long)
```

Standardizing the State Names

```{r}
predictor_df <- predictor_df %>%
  mutate(State = gsub("Chhattisgarh", "Chattisgarh", State)) %>%
  mutate(State = gsub("A & N ISLANDS", "Andaman and Nicobar Islands", State)) %>%
  mutate(State = gsub("D & N HAVELI", "Dadra and Nagar Haveli", State)) %>%
  mutate(State = gsub("DAMAN & DIU", "Daman and Diu", State)) %>%
  mutate(State = gsub("DELHI (UT)", "Delhi", State)) %>%
  mutate(State = gsub("Orissa", "Odisha", State)) %>%
  mutate(State = gsub("TOTAL (ALL INDIA)", "India", State))

# Check the result
unique(predictor_df$State)


```


```{r}
library(writexl)
write_xlsx(predictor_df, "predictor_data.xlsx")

```

```{r}
write_xlsx(accidents_long, "accidents_data.xlsx")
```


## End of data processing for Accidents and Predictors Data







